---
title: "AB Testing and Regression Analysis"
author: "Matteo Montrucchio"
date: "2024-04-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AB Testing
In the following file, I will evaluate the effectiveness of featuring actions.
I will analyze a dataset characterized by weekly sales and prices of orange juices across different stores for three brands. To evaluate the effectiveness of featuring actions, I compare the average sales by feat category.


```{r include=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org/"))
install.packages("tinytex")
tinytex::install_tinytex(force = TRUE)

```
```{r include=FALSE}
library(dplyr)
library(ggplot2)
```


```{r}
library(readr)
oj.data <- read_csv("/Users/matteomontrucchio/Desktop/oj_data.csv", show_col_types = FALSE)
```


```{r cars}
# show the first rows of the dataset
head(oj.data)
```

```{r}
# summarize the information contained in the dataset
summary(oj.data)
```

```{r}
# generate the plot comparing average sales by feat category and their SD
oj.data %>%
  mutate(feat= as.factor(feat)) %>%     # from the summary(), feat is stored as numeric variable
  group_by(feat) %>%                    
  summarise(Average = mean(sales),
            SD = sd(sales)) %>%
  ggplot(aes(feat,Average)) + 
  geom_point(size=5) +
  geom_errorbar(aes(ymin=Average-SD, ymax=Average+SD), width=.2) 
```

```{r}
t.table <- oj.data %>%
  mutate(feat= as.factor(feat)) %>%
  group_by(feat) %>%
  summarise(Average = mean(sales),
            Var = var(sales),
            N = n())
t.table
```

```{r}
t.test(oj.data[oj.data$feat==1, 1], oj.data[oj.data$feat==0, 1], var.equal=FALSE)
```
The data provided shows how average sales are higher when the product is featured.

On average, 40590 quantities are sold when product is featured against an average of 10071 quantities sold when not featured, resulting in an average difference of 30519 quantities (with a 95% probability, a store will sell between 29443.16 and 31594.84 more quantities).


## Regression
The goal is now to evaluate the effect that a price change has on the sales.

I will at first perform a simple linear regression analysis not considering the featuring.
```{r}
# plot sales VS price for feat equal to 0
ggplot(oj.data%>% filter(feat==0),aes(price,sales))+geom_point()+
  geom_smooth(method='lm',formula=y~x)
```

```{r}
# summary of the model
summary(lm(sales~price, oj.data %>% filter(feat==0) ))
```
This highlights how an increase in price of one unit has a negative effect on the average weekly sales that will reduce of 5522.5 units (more precisely, with a 95% level of confidence, between 5747.312 and 5297.688)

I will now run a second model in which I include the featuring effect in order to see if in the first model there was omitting variable bias.
```{r}
no.ovb <- lm(sales~price+feat, oj.data)
summary(no.ovb)
```
Considering the featuring effect, the estimated decrease in sales is of 10399 (95% C.I.: between 9965.256 and 10833.144).
